Evolution of pre-copulatory and post-copulatory inbreeding behaviour

### 2016-09-26 ms_pre_post.Rmd
Revise Model analysis section

To test our hypothesis that selection for polyandry is driven by a female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve given $c_{P} = \{0, 0.0025, 0.005}$. To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship (i.e, $F_{p}=0$). Hence, while mutation and drift can still occur for $F_{a}$ alleles, these alleles have no phenotypic effect and polyandry cannot cause polyandrous females to benefit through an increased ability to bias fertilisation toward inbreeding avoidance. By comparing evolution of mean $P_{p}$ values over generations when $F_{p}$ also evolves versus when $F_{p}=0$ (random fertilisation), we test whether or not evolution of post-copulatory inbreeding strategy increases selection for polyandry.

@@

<!--- TODO: NEED TO DO THESE SIMULATIONS ASAP --->
To test the hypothesis that selection for a costly strategy of inbreeding avoidance will be negligible given a less costly alternative strategy, we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and where $c_{F}=0$ but $c_{M}=0.02$. We contrast these simulations with evolution of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$). A contrast between the baseline expectation for how costs affect evolution of a focal inbreeding strategy in the absence of an alternative strategy, and evolution of a focal strategy given that an alternative strategy also evolves, tests whether or not a relatively low cost alternative strategy decreases selection for a focal strategy.

@@

To test the hypothesis that the existence of an adaptive inbreeding strategy will decrease the strength of selection on, and thereby preclude the invasion of, a complementary strategy, we first used exploratory simulations to determine evolution of precopulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation. To test whether or not pre-copulatory inbreeding avoidance was predicted to evolve when adaptive polyandry to avoid inbreeding was already established, we initiated pre-copulatory inbreeding strategy allele values at zero ($M_{a}=0$), but fixed post-copulatory inbreeding allele values at $F_{a}=-10$ and polyandry allele values at $P_{a}=1$ (i.e., $F_{p}$ and $P_{p}$ did not evolve). Similarly, to test whether or not inbreeding fertilisation strategy evolved to avoid inbreeding, we initiated inbreeding fertilisation strategy allele values and polyandry allele values at zero ($F_{a}=0$; $P_{a}=0$), but fixed inbreeding mating strategy allele values at $M_{a}=-10$.

>>>>

To test our hypothesis that selection for polyandry is driven by a female's ability to bias fertilisation toward inbreeding avoidance through post-copulatory mechanisms, we compare simulations in which all three phenotypes including tendency for polyandry ($P_{p}$), pre-copulatory inbreeding strategy ($M_{p}$), and post-copulatory strategy ($F_{p}$) evolve, with an identical set of simulations in which $F_{p}$ cannot evolve given $c_{P} = \{0, 0.0025, 0.005,  0.01\}$. To stop $F_{p}$ from evolving, we sever the connection from $F_{a}$ to $F_{p}$ such that all $F_{g}$ genotypes resulting from $F_{a}$ cause random fertilisation with respect to kinship (i.e, $F_{p}=0$). Hence, while mutation and drift can still occur for $F_{a}$ alleles, these alleles have no phenotypic effect and polyandry cannot cause polyandrous females to benefit through an increased ability to bias fertilisation toward inbreeding avoidance. By comparing mean $P_{a}$ values over generations when post-copulatory inbreeding avoidance also evolves versus when fertilisation is random, we test whether or not evolution of post-copulatory inbreeding strategy increases selection for polyandry.

@@

To test the hypothesis that selection for a costly strategy of inbreeding avoidance will be negligible given a less costly alternative strategy, we quantify change in $M_{a}$ and $F_{a}$ over generations in simulations where the cost of pre-copulatory inbreeding strategy $c_{M}=0$ but the cost of post-copulatory inbreeding strategy $c_{F}=0.02$, and where $c_{F}=0$ but $c_{M}=0.02$. We contrast these simulations with evolution of a costly strategy in the absence of evolution of an alternative strategy (e.g., evolution of pre-copulatory inbreeding strategy when post-copulatory inbreeding strategy phenotype is fixed at zero, $F_{p}=0$). A contrast between the baseline expectation for how costs affect evolution of a focal inbreeding strategy in the absence of an alternative strategy, and evolution of a focal strategy given that an alternative strategy also evolves, tests whether or not a relatively low cost alternative strategy decreases selection for a focal strategy.

@@

To test the hypothesis that the existence of an adaptive inbreeding strategy will decrease the strength of selection on, and thereby preclude the invasion of, a complementary strategy, we first used exploratory simulations to determine evolution of precopulatory inbreeding strategy, and post-copulatory inbreeding strategy and associated polyandry, in isolation. To test whether or not pre-copulatory inbreeding avoidance was predicted to evolve when adaptive polyandry to avoid inbreeding was already established, we initiated pre-copulatory inbreeding strategy allele values at zero ($M_{a}=0$), but fixed post-copulatory inbreeding allele values at $F_{a}=-10$ and polyandry allele values at $P_{a}=1$ (i.e., $F_{p}$ and $P_{p}$ did not evolve). Similarly, to test whether or not post-copulatory inbreeding strategy evolved to avoid inbreeding, we initiated post-copulatory inbreeding strategy allele values and polyandry allele values at zero ($F_{a}=0$; $P_{a}=0$), but fixed pre-copulatory inbreeding strategy allele values at $M_{a}=-10$. For reference, because females have 10 diploid loci, when $M_{a}$ or $F_{a}$ alleles were fixed at $-10$, outbred females were $51$ times less likely to choose a full sibling and $13.5$ times times less likely to choose a first cousin than a non-relative in pre- and post-copulatory choice, respectively.
